Sound and Automated Synthesis of Digital Controllers for Continuous Plants

### 2017-03-19 slides/presentation.tex
pres
counterexample fix
fixes to Abstraction CEGIS

\usepackage{url}           % format URLs
\usepackage{listings}      % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
\usepackage{enumitem}      % adjust spacing in enums
%\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
%\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{epstopdf}

@@

   \only<1,22>{\path (verif2) edge node {} (done);}
   \only<1>{\path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);}
   \only<2-7,16-17>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$} ([xshift=5em]gp.north);}
   \only<1-2,8,16,18>{\path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);}
   \only<3-7,17>{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=-5em]synth.south);}
   \only<1-3,8-9,16,18>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);}
   \only<4-7,17>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([yshift=2em]verif1.west);}
   \only<1-4,8-10,16,18-19>{\path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);}
   \only<5-7,17>{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=5em]bmc.north);}
   \only<1-5,8-11,16,18-19>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);}
   \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
   \only<1-6,8-12,16,18-19>{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
   \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
   \only<8-15>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=5em]gp.north);}
   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=-5em]synth.south);}
   \only<10-15>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}}$} ([yshift=2em]verif1.west);}
   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]bmc.north);}
   \only<12-15,20->{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {\textcolor{blue}{UNSAT}\\\textcolor{blue}{Pass}} ([xshift=-5em]verif1.south);}
   \only<1-12,16-20>{\path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);}
   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]fp.north);}
   \only<1-13,16-20>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);}
   \only<14-15>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{False}} ([xshift=-5em]verif2.south);}
   %\only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
   \only<17>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=-5em]verif1.south);}
   \only<17>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([yshift=-2em]synth.east);}
   \only<18->{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=5em]gp.north);}
   \only<19->{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}}$} ([yshift=2em]verif1.west);}
   \only<21->{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{True}} ([xshift=-5em]verif2.south);}

@@

\begin{frame}[fragile]{Completeness Bound}
\begin{figure}[t]
\centering
\includegraphics[width=0.6\textwidth]{ct.eps}
\vspace{0.1cm}
\label{fig:ct}
\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Case Study}
\begin{figure}
\centering
{\scriptsize
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=1.5cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=3.5cm] (verify) {\sc 3. verify ($\phi$)};
         \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc \textcolor{blue}{PASS}};

   \\
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
  };
  \only<1-3>{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\\k=0\end{array}}$} (synth.north);}
  \only<4->{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} (synth.north);}
    \only<1,4>{\path ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west);}
    \only<2-3,5->{\path ([yshift=1em]synth.east) edge node {$\textcolor{blue}{K}$} ([yshift=1em]verify.west);}
    \path (aux) edge (abstract.east);
  \only<1-3>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\end{array}}$} ([xshift=0.6cm]synth.south);}
  \only<4->{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} ([xshift=0.6cm]synth.south);}
    \only<1>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
    \only<2-3>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.24609375\\-0.125\\0.1484375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
    \only<4>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
    \only<5->{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.23828125\\-0.17578125\\0.109375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
    \only<1-2,4>{
    \path ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west);
    \path ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east);
    \path (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south);
    \path ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
    }
    \only<3,5->{
    \path ([yshift=.5cm]AAV.east) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([yshift=.5cm]AAC.west);
    \path ([yshift=-.5cm]AAC.west) edge node{$\textcolor{blue}{(k,x_0)}$} ([yshift=-.5cm]AAV.east);
    \path (AAC.north) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([xshift=4.9cm]verify.south);
    \path ([xshift=-5cm]verify.south) edge node{$\textcolor{blue}{K}$} (AAV.north);
    }

  \only<1-2,5->{\path[-] (verify.north) edge node {$(k,x_0)$} (aux);}
  \only<3-4>{\path[-] (verify.north) edge node {$\tiny \textcolor{blue}{\left(\begin{array}{cc}2,&[\begin{array}{ccc}.9&-.9&.9\end{array}]\\3,&[\begin{array}{ccc}.9&-.9&-.9\end{array}]\end{array}\right)}$} (aux);}
\end{tikzpicture}
}
\end{figure}
\end{frame}

>>>>

\usepackage{url}           % format URLs
\usepackage{listings}      % format code
\lstset{
  mathescape, 
  language={C},
  basicstyle=\small
}
%\usepackage{enumitem}      % adjust spacing in enums
%\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}   
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{xspace,framed}
\usepackage{colortbl}
\usepackage{calc}
%\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb,amsmath,amsfonts} 
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{epstopdf}

@@

   \only<1,22>{\path (verif2) edge node {} (done);}
   \only<1>{\path ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north);}
   \only<2-7,16-17>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$} ([xshift=5em]gp.north);}
   \only<1-2,8,16,18>{\path ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south);}
   \only<3-7,17>{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=-5em]synth.south);}
   \only<1-3,8-9,16,18>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west);}
   \only<4-7,17>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([yshift=2em]verif1.west);}
   \only<1-4,8-10,16,18-19>{\path  ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north);}
   \only<5-7,17>{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\frac{0z^2+0z+0}{0z^2+0z+0}}$} ([xshift=5em]bmc.north);}
   \only<1-5,8-11,16,18-19>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south);}
   \only<6-7>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=-5em]verif1.south);}
   \only<1-6,8-16,18->{\path ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east);}
   \only<7>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([yshift=-2em]synth.east);}
   \only<8-15>{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026506}{1.000610z+1.002838}}$} ([xshift=5em]gp.north);}
   \only<9-15,19->{\path ([xshift=-5em]gp.north) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=-5em]synth.south);}
   \only<10-15>{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}}$} ([yshift=2em]verif1.west);}
   \only<11-15,20->{\path  ([xshift=5em]verif1.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]bmc.north);}
   \only<12-15,20->{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {\textcolor{blue}{UNSAT}\\\textcolor{blue}{Pass}} ([xshift=-5em]verif1.south);}
   \only<1-12,16-20>{\path ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north);}
   \only<13-15,21->{\path ([xshift=5em]verif2.south) edge node[align=center] {$\textcolor{blue}{\hat{C}(z)}$} ([xshift=5em]fp.north);}
   \only<1-13,16-20>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south);}
   \only<14-15>{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{False}} ([xshift=-5em]verif2.south);}
   %\only<15>{\path ([yshift=-2em]verif1.west) edge node {\textcolor{blue}{precision}} ([yshift=-2em]synth.east);}
   \only<17>{\path  ([xshift=-5em]bmc.north) edge node[align=center]  {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=-5em]verif1.south);}
   \only<17>{\path ([yshift=-2em]verif1.west) edge node {$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([yshift=-2em]synth.east);}
   \only<18->{\path ([xshift=5em]synth.south) edge node[align=center] {$\textcolor{blue}{\frac{0.0264}{z-0.9998}}$\\$\textcolor{blue}{\frac{0.026314}{0.999024z{-}1.004785}}$} ([xshift=5em]gp.north);}
   \only<19->{\path ([yshift=2em]synth.east) edge node[xshift=-0.5em] {$\textcolor{blue}{\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}}$} ([yshift=2em]verif1.west);}
   \only<21->{\path  ([xshift=-5em]fp.north) edge node[align=center]  {\textcolor{blue}{True}} ([xshift=-5em]verif2.south);}

@@

\begin{frame}[fragile]{Completeness Bound/Threshold}
\begin{figure}[t]
\centering
\includegraphics[width=0.6\textwidth]{./figures/ct.pdf}
\vspace{0.1cm}
\label{fig:ct}
\end{figure}
\end{frame}

@@

\begin{frame}[fragile]{Case Study}
\begin{figure}
\centering
{\scriptsize
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=1.5cm, column sep=2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=3.5cm] (verify) {\sc 3. verify ($\phi$)};
        \uncover<9>{ \node[draw=none] (SAT) at ([xshift=2.2cm,yshift=-.3cm]verify)  {\sc \textcolor{blue}{PASS}};}

   \\
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
  };
  \only<1-5>{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\\k=0\end{array}}$} (synth.north);}
  \only<6->{\path (abstract.south) edge node{$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} (synth.north);}
    \only<1-2,6>{\path ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west);}
    \only<3-5,7->{\path ([yshift=1em]synth.east) edge node {$\textcolor{blue}{K}$} ([yshift=1em]verify.west);}
    \path (aux) edge (abstract.east);

  \only<1,6>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$(\phi(K),k)$} ([xshift=0.6cm]synth.south);}
  \only<2-5>{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{init}^K\\P_a(z)\end{array}}$} ([xshift=0.6cm]synth.south);}
  \only<7->{\path ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {$\textcolor{blue}{\begin{array}{c}\phi_{k,x_0}^K\\P_a(z)\\k=0,1,2\end{array}}$} ([xshift=0.6cm]synth.south);}
    \only<1-2,6>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$K$} ([xshift=-.6cm]KSAT.north);}
    \only<3-5>{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.24609375\\-0.125\\0.1484375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
    \only<7->{\path ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {$\textcolor{blue}{\left[\begin{array}{c}0.23828125\\-0.17578125\\0.109375\end{array}\right]^T}$} ([xshift=-.6cm]KSAT.north);}
    \only<1-3,6-7>{
    \path ([yshift=.5cm]AAV.east) edge node{\sl $\hat{X}^\#$} ([yshift=.5cm]AAC.west);
    \path ([yshift=-.5cm]AAC.west) edge node{$(k,x_0)$} ([yshift=-.5cm]AAV.east);
    \path (AAC.north) edge node{\sl $\hat{X}^\#$} ([xshift=4.9cm]verify.south);
    \path ([xshift=-5cm]verify.south) edge node{$K$} (AAV.north);
    }
    \only<4-5,8->{
    \path ([yshift=.5cm]AAV.east) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([yshift=.5cm]AAC.west);
    \path ([yshift=-.5cm]AAC.west) edge node{$\textcolor{blue}{(k,x_0)}$} ([yshift=-.5cm]AAV.east);
    \path (AAC.north) edge node{\sl $\textcolor{blue}{\hat{X}^\#}$} ([xshift=4.9cm]verify.south);
    \path ([xshift=-5cm]verify.south) edge node{$\textcolor{blue}{K}$} (AAV.north);
    }

  \only<1-4,7->{\path[-] (verify.north) edge node {$(k,x_0)$} (aux);}
  \only<5-6>{\path[-] (verify.north) edge node {$\tiny \textcolor{blue}{\left(\begin{array}{cc}2,&[\begin{array}{ccc}.9&-.9&.9\end{array}]\\3,&[\begin{array}{ccc}.9&-.9&-.9\end{array}]\end{array}\right)}$} (aux);}
\end{tikzpicture}
}
\end{figure}
\end{frame}
